---
title: "| RESEARCH PROTOCOL\n| \n| Adverse Events of Special Interest within COVID-19 Subjects\n"
fontsize: 12pt
geometry: margin=1in
output:
  bookdown::html_document2:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
    number_tables: yes
    css: "style.css"
  bookdown::word_document2:
    toc: yes
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: xelatex
    md_extensions: +raw_attribute
    number_sections: yes
    # citation_package: natbib
    includes:
      before_body: title.tex
header-includes:
- \usepackage[numbers,sort&compress]{natbib}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{caption}
- \usepackage{rotating}
- \usepackage{multirow}
- \usepackage{mwe,tikz}
- \usepackage[percent]{overpic}
- \usepackage{enumitem}
- \usepackage{hyperref}
- \newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
- \newcommand{\footerDate}{`r params$date`}
- \input{header.tex}
longtable: yes
mainfont: Arial
bibliography: Protocol.bib
params:
  date: '2021-10-29☻'
  version: 0.0.1
subtitle: 'Version: `r params$version`'
link-citations: true
csl: bmj.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
#knitr::knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage[table]{xcolor}', x, fixed = TRUE)})
library(dplyr)
options(knitr.kable.NA = "")
if (!knitr::is_latex_output() && !knitr::is_html_output()) {
  options(knitr.table.format = "simple")
}

library(Covid19SubjectsAesiIncidenceRate)

latex_table_font_size <- 8


```

# List of Abbreviations

```{r abbreviations, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
abbreviations <- readr::read_delim(col_names = FALSE, delim = ";", trim_ws = TRUE, file = "
  AESI; adverse events of special interest 
  CCAE; IBM MarketScan(R) Commercial Claims and Encounters
  CDM; Common Data Model
  COVID-19; COronaVIrus Disease 2019
  CPRD; Clinical Practice Research Datalink
  CUIMC; Columbia University Irving Medical Center 
  DA; Disease Analyzer
  EHR; Electronic Health Record
  EHDEN; European Health Data & Evidence Network
  FDA; U.S. Food and Drug Administration 
  JMDC; Japan Medical Data Center
  MDCD; IBM MarketScan(R) Multi-State Medicaid Database 
  MDCR; IBM MarketScan(R) Medicare Supplemental Database
  OHDSI; Observational Health Data Science and Informatics
  OMOP; Observational Medical Outcomes Partnership
  OPTUM_DOD; Optum(R) de-identified Clinformatics® Data Mart Database – Date of Death 
  OPTUM_EHR; Optum(R) de-identified Electronic Health Record Dataset 
  TAR; time-at-risk
  TTS; thrombosis with thrombocytopenia syndrome 
")

tab <- kable(abbreviations, col.names = NULL, linesep = "", booktabs = TRUE)

if (knitr::is_latex_output()) {
  tab %>% kable_styling(latex_options = "striped", font_size = latex_table_font_size)
} else {
  tab %>% kable_styling(bootstrap_options = "striped")
} 
```

# Responsible Parties

## Investigators

```{r parties, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
parties <- readr::read_delim(col_names = TRUE, delim = ";", trim_ws = TRUE, escape_backslash = TRUE, file = "
  Investigator; Institution/Affiliation
  Erica A Voss *; Observational Health Data Analytics, Janssen Research and Development, Titusville, NJ, USA
  Azza Shoaibi; Observational Health Data Analytics, Janssen Research and Development, Titusville, NJ, USA
  Anna Ostropolets; Department of Biomedical Informatics, Columbia University Irving Medical Center, New York, NY, USA
  Fredrik Nyberg; School of Public Health and Community Medicine, Institute of Medicine, Sahlgrenska Academy, University of Gothenburg, Gothenburg, Sweden
  Thamer Alshammary; Medication Safety Research Chair, King Saud University, Riyadh, Saudi Arabia
  Marc A. Suchard; Department of Biostatistics, University of California, Los Angeles, Los Angeles, CA, USA
  Martijn J. Schuemie ; Observational Health Data Analytics, Janssen Research and Development, Titusville, NJ, USA
  Dani Prieto-Alhambra; Centre for Statistics in Medicine, NDORMS, University of Oxford, Oxford, UK
  Peter R Rijnbeek ; Erasmus University Medical Center, Rotterdam, The Netherlands
  Patrick B Ryan; Observational Health Data Analytics, Janssen Research and Development, Titusville, NJ, USA
")

tab <- kable(parties, booktabs = TRUE, linesep = "") %>% 
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "30em") %>%
  footnote(general = "* Principal Investigator", general_title = "")

if (knitr::is_latex_output()) {
  tab %>% kable_styling(latex_options = "striped", font_size = latex_table_font_size)
} else {
  tab %>% kable_styling(bootstrap_options = "striped")
}
```

## Disclosures

This study is undertaken within Observational Health Data Sciences and Informatics (OHDSI), an open collaboration.

Data sources associated with the EHDEN network received funding from the Innovative Medicines Initiative 2 Joint Undertaking (JU) under grant agreement No 806968. The JU receives support from the European Union’s Horizon 2020 research and innovation programme and EFPIA.

**EAV**, **AS**, **MJS**, and **PBR** are employees Janssen Research & Development, LLC and are Johnson & Johnson shareholders.

**MAS** receives grant funding from the US National Institutes of Health and the US Food & Drug Administration and contracts from the US Department of Veterans Affairs and Janssen Research and Development.

# Amendments and Updates

Table \@ref(tab:amendments) lists any protocol amendments made over time.

```{r amendments, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
amendments <- readr::read_delim(col_names = TRUE, delim = ";", trim_ws = TRUE, file = "
  Number; Date; Section of study protocol; Amendment or update; Reason
  -;-;-;-;-
")

tab <- kable(amendments, booktabs = TRUE, linesep = "", caption = "Protocol amendments")

if (knitr::is_latex_output()) {
  tab %>%
    column_spec(1, width = "4em") %>%
    column_spec(2, width = "6em") %>%
    column_spec(3, width = "10em") %>%
    column_spec(4, width = "15em") %>%
    column_spec(5, width = "15em") %>%
    kable_styling(latex_options = "striped", font_size = latex_table_font_size)

} else {
  tab %>% kable_styling(bootstrap_options = "striped")
}
```

# Milestones

Table \@ref(tab:dates) lists the study milestones.

```{r dates, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
dates <- readr::read_delim(col_names = TRUE, delim = ";", trim_ws = TRUE, file = "
  Milestone; Planned / actual date
  Start of analysis;2021-11-29
  End of analysis;2021-12-31
  Results presentation;2021-02-01
")

tab <- kable(dates, booktabs = TRUE, linesep = "", caption = "Study milestones") 

if (knitr::is_latex_output()) {
  tab %>% kable_styling(latex_options = "striped", font_size = latex_table_font_size)
} else {
  tab %>% kable_styling(bootstrap_options = "striped")
}
```

# Rationale and Background

Background rates of adverse events are important in monitoring the safety of vaccines as this baseline information can serve as a comparator to the rates of the adverse events in those that are vaccinated [@Black2006] [@Wijnans2013]. Previously, the Observational Health Data Sciences and Informatics (OHDSI) community conducted a population-based network retrospective cohort study to characterize the background rates of adverse events of special interest (AESI) for the COVID-19 vaccine, using observational data from 13 databases in 8 countries [@Li2021]. This work extends this prior OHDSI study by characterizing the background rates of these AESIs in subjects after their COVID-19 disease. In addition to pre-pandemic rates in the general population, it is relevant to know how often these AESIs occur amongst patients who suffer the condition vaccines aim to prevent to provide a counterfactual for risk evaluation.

# Study Objectives

We aim to quantify how often AESIs occur in subjects post COVID-19 disease overall and across specific age and sex groups.

Our aim is purely descriptive. The hope with this work is the evidence we provide can be used to contextualize safety signals among the vaccinated and also inform risk benefit analysis

# Research Methods

## Data Sources
We intend to study data with different data source provenance (e.g., electronic medical records, insurance claims) as well data representing different populations (privately insured employees or patients with limited income) and data with different origins (US and non-US).  This study will be run on datasets that have been converted to the Observational Medical Outcomes Partnership (OMOP) Common Data Model (CDM) [@OMOPCDM-wp] [@Hripcsak2015-cl]. 

These data sources include but are not limited to: 

- Columbia University Irving Medical Center (CUIMC) Electronic Health Record (EHR) 
- Stanford 
- IBM MarketScan® Commercial Claims and Encounters (CCAE) 
- IBM MarketScan® Medicare Supplemental Beneficiaries (MDCR) 
- IBM MarketScan® Multi-state Medicaid (MDCD) 
- IQVIA® Disease Analyzer (DA) Germany (IQVIA_GERMANY_DA) 
- IQVIA® Disease Analyzer (DA) France (IQVIA_FRANCE_DA) 
- IQVIA® Australia Australia Longitudinal Patient Data (IQVIA_AUSTRALIA_LPD) 
- Japan Medical Data Center (JMDC) 
- Optum® de-identified Electronic Health Record Dataset (OPTUM_EHR) 
- Optum® de-identified Clinformatics® Data Mart Database – Date of Death (OPTUM_DOD) 
- Clinical Practice Research Datalink (CPRD) – GOLD / Aurum  
- Various European Health Data & Evidence Network (EHDEN) Data Partners 
- Other data sources from prospective data partners  

## Study Populations
We will define all target and outcome cohorts in the Atlas environment ([https://atlas.ohdsi.org/](https://atlas.ohdsi.org/)). Detailed definitions can be found in the Appendix.

### Target Cohort Definitions
The target population is subjects who had COVID-19 disease. We will identify this in two ways:

 - COVID-19 Identified by the First of COVID-19 positive test or Diagnosis (without a negative test) 
 - COVID-19 Identified by COVID-19 positive test
 
### Outcome Cohort Definitions
For the purposes of this research, we use the outcomes outlined in the U.S. Food and Drug Administration (FDA) “Background Rates of Adverse Events of Special Interest for COVID-19 Vaccine Safety Monitoring” protocol [6]. This protocol includes Guillain-Barré syndrome, facial nerve (Bell’s) palsy, anaphylaxis, encephalomyelitis, narcolepsy, appendicitis, non-hemorrhagic stroke, hemorrhagic stroke, acute myocardial infarction, myocarditis and pericarditis, deep vein thrombosis, pulmonary embolism, disseminated intravascular coagulation, immune thrombocytopenia, febrile seizure, and transverse myelitis. We will also include additional safety outcomes/concerns that emerged such as thrombosis with thrombocytopenia syndrome (TTS), seizure, and narcolepsy. All phenotype definitions were based on the FDA protocol (when possible) with minor clinical context broadening (and minor code broadening as needed for example to accommodate SNOMED) to allow them to run on our wide range of data sources. 

We consider the effect of clean windows to define the incidence of outcomes. A clean window is the prespecified time prior to the vaccination (reference master protocol [@COVID19AESIs]). We will use an outcome-specific clean window, within which an outcome is not considered incident. The clean window (as also defined in the FDA protocol), is 365 days for all outcomes except 30 days for anaphylaxis, 183 days for facial nerve palsy and encephalomyelitis.  

- Cohort 411 - FDA AESI Pulmonary Embolism events with conceptset subsuming FDA source concepts
- Cohort 405 - FDA AESI Hemorrhagic stroke IP events with conceptset subsuming FDA source concepts
- Cohort 406 - FDA AESI non-hemorrhagic stroke IP events with conceptset subsuming FDA source concepts
- Cohort 402 - FDA AESI Deep Vein Thrombosis (DVT) events with conceptset subsuming FDA source concepts
- Cohort 386 - FDA AESI Appendicitis events
- Cohort 385 - FDA AESI Disseminated intravascular coagulation events
- Cohort 381 - FDA AESI Transverse myelitis events
- Cohort 349 - FDA AESI Anaphylaxis events
- Cohort 347 - FDA AESI Bells palsy events
- Cohort 346 - FDA AESI Encephalomyelitis IP events
- Cohort 345 - FDA AESI Narcolepsy events
- Cohort 343 - FDA AESI Guillain Barre syndrome IP events
- Cohort 340 - FDA AESI Acute myocardial infarction IP events
- Cohort 339 - FDA AESI Myocarditis Pericarditis events
- Cohort 335 - FDA AESI Immune thrombocytopenia (ITP) events
- Cohort 547 - [TwT] Thrombosis (Narrow diagnosis) with Thrombocytopenia (narrow diagnosis or measurement) events

## Population Subgroups
In order to appropriately use incidence characterization among a target population (e.g., COVID-19 subjects) as context for interpreting an observed rate of adverse events in a given population (e.g., a population exposed to COVID-19 vaccines), it is important to consider the extent to which the target population is comparable to the exposed individuals.  

One aspect of the target population is the population subgroup. We will consider the following age and sex subgroups independently and jointly. 

- Age groups 
  - High Risk of Severe COVID-19: 
    - 18-64  
  - Pediatric Age Groups: 
    - 0-4 
    - 5-11 
    - 12-17 
  - General: 
    - 0–5 
    - 6–17 
    - 18–35 
    - 36–55 
    - 56–64 
    - 65–74 
    - 74–85 
    - Greater Than 85 
  - Sex 
    - Male 
    - Female 

## Time-at-risk (TAR)
For AESI rates estimated for a general population, TAR is not possible to take into account, since there is no obvious index point from which TAR would be counted. Consequently AESI rates estimated over moderately long time intervals are for statistical stability is generally an appropriate approach to give background rates. When trying to understand AESI in COVID-19 patients, in contrast, the onset of COVID-19 provides a natural index point, which may be directly relevant if the AESI is associated with COVID-19. For some outcomes, there is a known pathophysiological relationship between them and COVID-19 that can justify a choice of time at risk. For other outcomes, less is known. In estimating baseline incidence rates, there is a tension between using long time-at-risk windows to maximize the sample size and provide rate stability,  and using windows that match the planned windows in the vaccinated patients. Using windows that match the planned windows in vaccinated individuals would be relevant mainly for conditions where it may be possible that both COVID-19 and vaccination affect the outcome with similar TAR, which may be assumed to be the case mainly if they act through related or similar mechanisms. In other situations, the more relevant comparison or context may be stable long-term rates. AESI rates on COVID-19 individuals, for different TARs, will be particularly important to understand especially when AESIs are assessed in vaccinated individuals, where information on prior COVID-19 and its timing are available. 

We will include six TARs, relative to the COVID-19 index date, for this work. 

- Days 1 – 2 days (to capture acute events) 
- Days 1 – 14 days (to align with COVID-19 symptoms appearing [@COVID19Symptoms]) 
- Days 1 – 21 days (this will likely be the target TAR post vaccines) 
- Days 1 – 28 days 
- Days 1 – 90 days 
- Days 1 – 365 days 

## Incidence rate estimation outputs
The same cohort may address several questions, so they are grouped by cohort below. For each cohort, we compute the following: 

- Absolute number of outcomes 
- Absolute number of outcomes prior to TAR start date 
- Absolute number of patients at risk 
- Absolute number of patients with outcomes prior to TAR start date 
- Absolute number of patients with outcomes within TAR interval 
- Incidence proportion of outcomes within TAR interval 
- Incidence rate of outcomes within TAR interval 

In the above outcome counts, multiple data elements (e.g., multiple diagnosis codes) within a clean window count as one outcome. Patients will contribute time-at-risk from the index date (date of COVID-19 diagnosis or positive results) until the earliest of 365 days after the index, their observation period end date, or the start date of the outcome event. Persons with prior outcome events will not begin to contribute time-at-risk until the clean window requirement is satisfied.

We will generate descriptive statistics for all these cohorts using the OHDSI R tool called Cohort Diagnostics.  Additionally, incidence rates will be calculated via an R package.  



# Strengths and Limitations

## Strengths
- Cohort studies allow direct estimation of incidence rates following exposure of interest, and the new-user design can capture early events following treatment exposures while avoiding confounding from previous treatment effects; new use allows for a clear exposure index date.
- The fully specified study protocol is being published before analysis begins.
- Dissemination of the results will not depend on estimated effects, avoiding publication bias.
- All analytic methods have previously been verified on real data.
- All software is freely available as open source.
- Use of a common data model allows extension of the experiment to future databases and allows replication of these results on licensable databases that were used in this experiment, while still maintaining patient privacy on patient-level data.
- Use of multiple databases allows estimating consistency to add credibility and supports generalizability.

## Limitations
 
- Misclassification of study variables is unavoidable in secondary use of health data, so it is possible to misclassify treatments, covariates, and outcomes; we do not expect differential misclassification, so bias will most likely be towards the null.
- The electronic health record databases may be missing care episodes for patients due to care outside the respective health systems; bias will most likely be towards the null.
- Causality between drug exposure and any given event cannot be drawn for individual cases. 

# Protection of Human Subjects
This work does not involve human subjects research.The project does, however, use de-identified human data collected during routine healthcare provision. Confidentiality of subject records will be maintained always. All study reports will contain aggregate data only and will not identify individual subjects or physicians. At no time during the study will the sponsor receive subject identifying information except when it is required by regulations in case of reporting adverse events.

All data partners executing this study within their data sources will have received institutional review board (IRB) approval or waiver for participation in accordance to their institutional governance prior to execution. This study will be executed across a federated and distributed data network, where analysis code is sent to participating data partners and only aggregate summary statistics are returned, with no sharing of patient-level data between organizations.

# Management and Reporting of Adverse Events and Adverse Reactions

This study uses coded data that already exist in electronic databases. In these types of databases, it is not possible to link (i.e., identify a potential causal association between) a particular product and medical event for any specific individual.Thus, the minimum criteria for reporting an adverse event (i.e., identifiable patient, identifiable reporter, a suspect product and event) are not available and adverse events are not reportable as individual adverse event reports. The study results will be assessed for medically important findings.

# Plans for Disseminating and Communicating Study Results

Open science aims to make scientific research, including its data process and software, and its dissemination, through publication and presentation, accessible to all levels of an inquiring society, amateur or professional [@Woelfle2011-ss].
Open science delivers reproducible, transparent and reliable evidence.
All aspects of study (except private patient data) will be open and we will actively encourage other interested researchers, clinicians and patients to participate.

## Transparent and re-usable research tools

The protocol and all source code will be available here prior to execution across the federated and distributed network.
[https://github.com/ohdsi-studies/Covid19SubjectsAesiIncidenceRate](https://github.com/ohdsi-studies/Covid19SubjectsAesiIncidenceRate) 

## Continous sharing of results

We will store and openly communicate all of these results as they become available using a user-friendly web-based app.

## Scientific meetings and publications

We will deliver multiple presentations at scientific venues and will also prepare multiple scientific publications for clinical, informatics, and statistical journals.

## General public

We believe in sharing our findings that will guide clinical care with the general public. This study will use social-media (Twitter-[OHDSI](https://twitter.com/ohdsi)) to facilitate this. 

# References {-}

<div id="refs"></div>

# (APPENDIX) Appendix {-}

# Target Cohort Definitions
TBD

# Outcome Cohort Definitions

```{r pulmonaryEmbolism-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort411-pulmonaryEmbolism.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 411 - FDA AESI Pulmonary Embolism events with conceptset subsuming FDA source concepts",json = baseCohortJson)
```

```{r hemorrhagicStroke-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort405-hemorrhagicStroke.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 405 - -FDA AESI Hemorrhagic stroke IP events with conceptset subsuming FDA source concepts",json = baseCohortJson)
```


```{r nonHemorrhagicStroke-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort406-nonHemorrhagicStroke.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 406 - FDA AESI non-hemorrhagic stroke IP events with conceptset subsuming FDA source concepts",json = baseCohortJson)
```

```{r deepVein-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort402-deepVein.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 402 - FDA AESI Deep Vein Thrombosis (DVT) events with conceptset subsuming FDA source concepts",json = baseCohortJson)
```

```{r appendicitis-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort386-appendicitis.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 386 - FDA AESI Appendicitis events",json = baseCohortJson)
```

```{r disseminatedIntravascularCoagulation-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort385-disseminatedIntravascularCoagulation.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 385 - FDA AESI Disseminated intravascular coagulation events",json = baseCohortJson)
```

```{r transverseMyelitis-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort381-transverseMyelitis.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 381 - FDA AESI Transverse myelitis events",json = baseCohortJson)
```

```{r anaphylaxis-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort349-anaphylaxis.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 349 - FDA AESI Anaphylaxis events",json = baseCohortJson)
```

```{r bellsPalsy-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort347-bellsPalsy.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 347 - FDA AESI Bells palsy events",json = baseCohortJson)
```

```{r encephalomyelitis-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort346-encephalomyelitis.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 346 - FDA AESI Encephalomyelitis IP events",json = baseCohortJson)
```

```{r narcolepsy-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort345-narcolepsy.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 345 - FDA AESI Narcolepsy events",json = baseCohortJson)
```

```{r guillainBarre-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort343-guillainBarre.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 343 - FDA AESI Guillain Barre syndrome IP events",json = baseCohortJson)
```

```{r acuteMyocardialInfarction-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort340-acuteMyocardialInfarction.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 340 - FDA AESI Acute myocardial infarction IP events",json = baseCohortJson)
```


```{r myocarditisPericarditis-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort339-myocarditisPericarditis.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 339 - FDA AESI Myocarditis Pericarditis events",json = baseCohortJson)
```

```{r immuneThrombocytopenia-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort335-immuneThrombocytopenia.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 335 - FDA AESI Immune thrombocytopenia (ITP) events",json = baseCohortJson)
```


```{r twt-cohort, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
baseCohortJson <- SqlRender::readSql(system.file("cohorts", "Cohort547-twt.json", package = "Covid19SubjectsAesiIncidenceRate"))
baseCohort <- RJSONIO::fromJSON(baseCohortJson)

baseCohortJson <- RJSONIO::toJSON(baseCohort, digits = 50)

printCohortDefinitionFromNameAndJson(name = "Cohort 547 - TwT Thrombosis (Narrow diagnosis) with Thrombocytopenia (narrow diagnosis or measurement) events",json = baseCohortJson)
```
